Typechecking a linear \picalc

### 2020-02-09 paper/paper.tex
Some more notes

\begin{abstract}
  We present the syntax, operational semantics, and typing rules for a \picalc{} with linear and shared types. We use a typing with leftovers approach \cite{} to encode our typing rules. We build framing and weakening proofs that we then use to prove subject congruence and subject reduction.
\end{abstract}

@@

Goals: present nice model, prove subject reduction

@@

@@

using dependent types to encode typing rules

removing from context vs keeping in context but marking it used

two-layered approach: types on one hand, capabilities on the other

n multiplicities as a generalisation

@@

nat numbers + omega as a generalisation

@@

@@

@@

\subsection{Framing}
\subsection{Weakening}

>>>>

\begin{abstract}
  We present the syntax, operational semantics, and typing rules for a \picalc{} with linear and shared types. We use leftover typing \cite{} to encode our typing rules. We build framing and weakening proofs that we then use to prove subject congruence and subject reduction.
\end{abstract}

@@

@@

\subsection{Contribution}

machine verified formalisation of the pi calculus

typing with leftovers applied to the pi calculus

unique quirks: multiple multiplicities per variable, shared types

@@

\subsection{Variable references}

\begin{description}
  \item[Polarities]
  \item[Multiple variables]
  \item[Vectors]
    Most general solution, $n$ possible multiplicities
\end{description}

\subsection{Multiplicities}

$\inf$ and $\mathbb{N}$ as generalisations

@@

\subsubsection{Total definition}

\subsubsection{Partial definition}

@@

\subsection{Variable types and multiplicities}

two-layered approach: types on one hand, capabilities on the other
removing from context vs keeping in context but marking it used

@@

\subsubsection{Typing relation}

@@

\subsection{Framing}

Definition
Let $\Gamma \types P \boxtimes \Delta$ and $\Gamma - Delta \equiv \Xi - \phi$.
Then $\Xi \types P \boxtimes \phi$.

By defining of $\uplus$ as a total function, $\Gamma - \Delta$ is no longer
functional: $\omega - \omega$ results in any multiplicity, including $0$. Therefore
$\Xi \types P \boxtimes \phi$ would imply that such a variable cannot appear in $P$.

\subsection{Weakening}
